G\"{o}del's Ontological Proof of God's Existence (Draft)

### 2013-09-12 Natural Deduction/GodProof-ND.tex
Add draft definition of package

\usepackage{latexsym}
\usepackage{bussproofs}
\EnableBpAbbreviations
\newcommand{\rl}[1]{\RightLabel{#1}}

\newtheorem{axiom}{Axiom}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

@@

ToDo: Show and explain here the rules of the calculus we are using.

ToDo: We should use a calculus for the basic modal logic K. Everything else should be stated as axioms.

ToDo: Investigate the relationship between the $\nec_E$ rule and the $M$ axiom (reflexivity). We don't want $M$ to be provable in our calculus.

ToDo: cite a paper that proves soundness and completeness for this calculus.

>>>>

\usepackage{latexsym}
\usepackage{proof}
\usepackage{bussproofs}
\EnableBpAbbreviations
\newcommand{\rl}[1]{\RightLabel{#1}}

\usepackage{calculi}
\usepackage{theorems}

@@

\newcommand{\s}{\qquad}

\begin{calculus}
{The natural deduction calculus \ND}
{fig:ND}

\vspace{1em}

\s\s\s
\infer[\imp_I^n]{A \imp B}{ \infer*{B}{A^n} }
\s\s\s
\infer[\imp_E]{B}{A & A \imp B}

\vspace{2em}

\s\s
\infer[\wedge_I]{A \wedge B}{A & B}
\s\s
\infer[\wedge_{E_1}]{A}{A \wedge B}
\s\s
\infer[\wedge_{E_2}]{B}{A \wedge B}

\vspace{2em}

\s
\infer[\all_I]{\all x. A[x]}{ A[\alpha] }
\s
\infer[\all_E]{A[t]}{ \all x. A[x] }
\s\s
\infer[\ex_I]{\ex x. A[x]}{ A[t] }
\s
\infer[\ex_E]{A[\alpha]}{ \ex x. A[x] }

\vspace{1em}

ToDo: State eigen-variable conditions
\end{calculus}

\begin{calculus}
{\NDK: Rules for Modal Operators}
{fig:NDK}
\s\s\s
\infer[\nec_I]{\nec A}{A}
\s\s
\infer[\nec_E]{A}{\nec A}

\vspace{1em}

ToDo: state conditions
\end{calculus}
